The \raveon\ catalog of stellar atmospheric parameters and\\ chemical abundances for chemo-dynamic studies in the \gaia\ era

### 2016-09-09 article/unrave.tex
typos

\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Derived labels, associated errors, and relevant metadata are available electronically
through the \rave\ from 19 September 2016 onwards. Please note that it is a condition
of using these results that the fifth \rave\ data release by \citet{Kunder_2016} must 
also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.

>>>>

\noindent{}Source code for this project is available at \texttt{\giturl}\hspace{-0.5em},
and this document was compiled from revision hash \texttt{\githash} in that repository.
Derived labels, associated errors, and relevant metadata are available electronically
through the \rave\ database from 19 September 2016 onwards. Please note that it is a 
condition of using these results that the \rave\ data release by \citet{Kunder_2016} 
must also be cited, as the work presented here would not have been possible without the 
tireless efforts of the entire \rave\ collaboration, past and present.
